##DV Project 3

1) We found a data set (csv file) about Diabetes patients with thousands of rows of data as well as a few other associated data sets (csv files) . We then regiestered our data set type under the PROJECt_2DATA column using the "Register Your Project" link on the class website.

2) We loaded each CSV file into one of our Oracle accounts using a modified version of R_ETL.R.

3) We modified the query found in Titanic Analysis.R by changing the SQL statement and filled in one of our UTEids to build a data frame from our data from the primary Diabetes data set. We continued by adding each additional associated data set to their own dataframes in succession.

```{r}
source("../01 Data/Data.R", echo = TRUE)
```

```{r}
source("../01 Data/Data_Mortality.R", echo = TRUE)
```

```{r}
source("../01 Data/Data_MI.R", echo = TRUE)
```

```{r}
source("../01 Data/Data_Stroke.R", echo = TRUE)
```

```{r}
source("../01 Data/Data_Angina.R", echo = TRUE)
```

4) We wrangled the original Diabetes data along with the associated health data sets using 3 different data wrangling operations to combine data sets:
a. Inner Join of Diabetes with Mortality
b. Left Outer Join of Diabetes with MI and Stroke
c. Full Join of Diabetes with Angina

```{r}
source("../02 Data Wrangling/DataWrangling.R", echo = TRUE)
```

```{r}
source("../02 Data Wrangling/DataWranglingMIStroke.R", echo = TRUE)
```

```{r}
source("../02 Data Wrangling/DataWranglingAngina.R", echo = TRUE)
```

5) From those wrangled sets of data we produced the following 3 plots/visualizations of the associated data sets vs the original data so as to compare the outcomes and treatments of various diabetes patients alongside corresponding data concerning other associated conditions:


```{r}
source("../03 Visualizations/Visualization1.R", echo = TRUE)
```

As you can see with these graphs, diabetes does correlate to an additional risk of mortality.  However, neither increasing prevalence when considering all types of diabetes together nor when considering type 1 diabetes alone appear to be correlated with increasesd risk of mortality.  Only increasing prevalence of type 2 diabetes appears to be correlated with an increased risk for death.

```{r}
source("../03 Visualizations/Visualization2.R", echo = TRUE)
```

As you can see with these graphs, diabetes does correlate to an increase in risk for MI and stroke, but increasing prevalence of diabetes (all types) does not correlate with an increased risk of stroke nor with MIs.

```{r}
source("../03 Visualizations/Visualization3.R", echo = TRUE)
```

Increasing prevalence of any type of diabetes does not appear to be correlated with an increased risk for stroke throughout the regions as whole.